\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}  % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\usepackage{ragged2e}
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%

\pagestyle{fancy} % allows you to use the header and footer commands


\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{Multiscale Flow and Heat Transfer Modeling of Nuclear Systems} \rhead{E. Merzari et al.} \renewcommand{%
%\pagestyle{fancy} \lhead{Harnessing Exascale: First of a Kind High Fidelity Full Core Simulations} \rhead{E. Merzari et al.} \renewcommand{%
%\pagestyle{fancy} \lhead{Large Eddy Simulation of Rod bundle cores} \rhead{E. Merzari et al.} \renewcommand{%
\headrulewidth}{0.0pt}

\begin{center}
\bf {PERSONNEL JUSTIFICATION AND MANAGEMENT PLAN} \\
\end{center}
\vspace{-.25in}
\justify
{\noindent \bf{Personnel Justification}}

\noindent The personnel involved in this project have clearly defined and pre-assigned roles. The co-PIs will be responsible for coordinating simulation campaigns and executing the technical tasks associated with each research thrust. Elia Merzari will serve as Principal Investigator and will be responsible for overall project coordination and leadership of Thrust 2. David Reger will lead the modeling and simulation activities associated with Thrust 1. In addition to the senior personnel, three graduate students will support model development, verification, production simulations, and data analysis as needed. Two students will be based at Pennsylvania State University and one at the University of Illinois Urbana-Champaign.

\vspace{-.15in}
\begin{itemize}
\item \textbf{Elia Merzari} is the Principal Investigator and will be responsible for the overall coordination and management of the project. He has led numerous ALCC and INCITE projects and has extensive experience in large-scale computational thermal-fluids simulations on leadership-class computing systems. He will also oversee the activities associated with Thrust 2.

\item \textbf{Paul Fischer}, chief architect of Nek5000 and one of the principal developers of NekRS, will provide guidance on code optimization, meshing strategies, and large-scale simulation execution. He has led numerous INCITE projects, has more than 30 years of experience in high-performance computing, and is the recipient of both a Gordon Bell Award and an R\&D 100 Award.

\item \textbf{Misun Min} will coordinate project requirements with the CEED development team and will support extreme-scale testing, performance analysis, and code development activities. She serves as the Argonne National Laboratory PI for CEED and as the CEED liaison for the ExaSMR project. She was a recipient of the 2016 R\&D 100 Award for the development of the NekCEM/Nek5000 scalable high-order simulation codes.

\item \textbf{David Reger} is a member of the R\&D staff at Idaho National Laboratory and serves as the methods lead for the DOE-NE Gas Reactor Campaign. He will lead the modeling and simulation activities associated with Thrust 1.

\item \textbf{Graduate Student 1 (PSU) -- TBD} will support model development, verification, and production simulations for Thrust 1.

\item \textbf{Graduate Student 2 (PSU) -- TBD} will support model development, verification, and production simulations for Thrust 2.

\item \textbf{Graduate Student 3 (UIUC) -- TBD} will support model development and production simulations associated with the MHD activities.
\end{itemize}

{\noindent \bf{Management}}

\noindent As described above, all personnel have clearly defined responsibilities. The project leadership team, consisting of Elia Merzari, Paul Fischer, Misun Min, and David Reger, will meet bi-weekly via teleconference to review progress, discuss technical challenges, and monitor milestone completion. In addition, broader coordination meetings involving the full project team will be held twice annually to review accomplishments, assess resource utilization, and plan future activities.

\noindent As Principal Investigator, Elia Merzari will be responsible for overall project reporting and communication with the computing facilities. This includes tracking progress toward milestones, coordinating resource usage, and reporting project outcomes, including publications, presentations, software developments, and awards.

\noindent Each research task has a predefined allocation of computational resources and personnel. Graduate students will be supervised by the local principal investigator at their respective institutions, with Elia Merzari supervising students at Pennsylvania State University and Paul Fischer supervising students at the University of Illinois Urbana-Champaign. This structure ensures clear accountability while maintaining close coordination across all participating institutions.

\end{document}
