% LIMIT OF 15 PAGES!


\vspace{-.25in}
\subsection*{COMPUTATIONAL APPROACH} 
\vspace{-.2in}

We will perform the proposed simulations using NekRS which is a GPU-accelerated
version of Nek5000 (a Gordon Bell and R\&D 100 Prize winner \cite{tufo99a})
that is targeting high performance on forthcoming exascale platforms.  For
performance portability, NekRS is written in C++/OCCA \cite{occa}.  Several key
kernels come from the high-performance OCCA library, libParanumal
\cite{ChalmersKarakusAustinSwirydowiczWarburton2020,streamParanumal2020}, and
have been tailored and expanded to meet the specific requirements of NekRS. 
NekRS retains access to the standard Nek5000 interface, which allows users to
leverage existing user-specific source code such as statistical analysis tools
for turbulence.  NekRS, libParanumal, and OCCA were developed as part of
DOE's ECP in the Center for Efficient Exascale Discretizations (CEED).
NekRS was recognized as a 2023 Gordon Bell Finalist for sustaining $>$28 PFLOPS
as part of a suite of coupled fission/thermal-hydraulics simulations on 72,000
GCDs of Frontier \cite{gb23}.  

NekRS runs a battery of single-GPU tests at the start of each simulation
to identify the fastest kernel for each configuration.  These are measured by
using a combination of MPI\_Wtime and barriers.  A typical output is shown in
Table \ref{tab:log0}, which indicates (left to right) the operation, order,
precision, performance (GFLOPS), and the selected kernel version.   Inspection
of these tables is extremely useful in identifying under-performing kernels as
platforms evolve.
The data shown is from the largest runs with $N=10$ (1000 unknowns per
spectral element).
The operations are advection ({\tt adv}),
application of the discrete Laplacian ({\tt Ax})
and
solution of a local Poisson problem with the fast-diagonalization method
({\tt fdm}).  These are all tensor contractions involving $O(N^3)$ memory
references and $O(N^4)$ operations, per element.
Advection uses over-integration with a 3/2s rule and requires $\approx 40n$
loads and 8$Nn \times N_f$ operations, where $N_f=1$ or 3 is the number of
fields to be advected. The discrete Laplacian (\ref{eq:bk5x}) requires
$7(N+1)^3$ loads and $12(N+1)^4$ operations per element, while the FDM requires
$2(N+1)^3$ loads and $6(N+1)^4$ operations.
Note that {\tt Ax} and {\tt fdm} are used in the multilevel Schwarz
preconditioner \cite{malachi2022a} and thus require runtime-compiled versions for
each value of $N$ employed in the smoother.  These are of course run in FP32.
All of the $O(N^4)$ operations are effectively cast as BLAS3 {\em dgemms} in
the case of CPUs \cite{dfm02}, but are coded to exploit fine-grained
parellelism in the OCCA-based GPU kernels that are ultimately cast
to DPCPP, HIP, or CUDA depending on the target \cite{nekrs}.


In Table \ref{tab:log0}, we can see that a single MI250X GCD on Frontier
generally outperforms a single PVC Tile on Aurora, save for some of the
low-order {\tt fdm} calls.  (One MPI rank is assigned to each GCD or Tile.)
This performance difference is consistent with the relatively small cache
on the PVC.  Of the operations listed, the {\tt fdm}32 has the smallest
memory footprint, where as the de-aliased advection operator, {\tt adv}64
has the largest.  Despite these differences, it is remarkable that almost
all of the kernels sustain $>$ 1 TFLOPS, even for FP64.  It is also
worth noting that the NVIDIA H100 outperforms the single Tile/GCDs
by 2--3 $\times$.
%
We remark that, in addition to yielding optimal performance,
runtime kernel selection also avoids code regression as existing kernels
are never deleted from the source.

The setup phase of NekRS also measures and
reports communication overhead for each instantiation of the gather-scatter
operation (an unstructured equivalent to the ``halo exchange'' of finite
difference methods).  Possible variants include overlapping communication with
computation via the sequence: {\em compute surface elements, initiate exchange,
complete interior element computations, wait for incoming surface values and
finish}, or computing all the local residuals first, as in (\ref{eq:bk5x}), and
then exchanging.  Locally, the gather-scatter requires posting receives,
packing element surface data into contiguous outbound arrays, then sending
those.  Exchanges are effected using GPU-aware MPI
or by passing the data to the host, whichever is fastest during the
setup times unless the user elects to override the autotuned choice.

Each NekRS job also tracks basic runtime statistics, which are output every 500
time steps unless the user specifies otherwise.  Timing breakdowns roughly
follow the physical substeps of advection, pressure, and viscous update, plus
tracking of known communication bottlenecks.  In addition, each significant
kernel returns its flop count, so a precise (somewhat conservative) flop rate
is returned.  (In counting total flops, we assign a weight of 1/2 to fp32
operations.) These results are used in guiding performance optimization.
% and are illustrated in the next section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{-.25in}
\subsection*{PARALLEL PERFORMANCE}
\vspace{-.2in}

\noindent{\bf State-of-the-Art.}
Nek5000/RS is based on the spectral element method (SEM) \cite{pat84}, in which
functions are represented as $N$th-order polynomials on each of $E$ elements,
for a total mesh resolution of $n=EN^3$.  
The SEM offers many advantages for this class of problems.  It accommodates
body-fitted coordinates through isoparametric mappings domain from the
reference element, $\Oh:=[-1,1]^3$ to the individual (curvilinear-brick)
elements $\Omega^e$.  On $\Oh$, solutions are represented in terms of
$N$th-order tensor-product polynomials,
\begin{eqnarray} \label{eq:field1}
\left. {\bf u}({\bf x}) \right|^{}_{\Omega^e} = \sum_{i=0}^N
\sum_{j=0}^N \sum_{k=0}^N {\bf u}_{ijk}^{e}\,h_i(r)\,h_j(s)\,h_k(t),
\end{eqnarray}
where the $h_i$s are stable nodal interpolants based on the
Gauss-Lobatto-Legendre (GLL) quadrature points $(\xi_i,\xi_j,\xi_j)\in \Oh$
and ${\bf x}={\bf x}^e(r,s,t)$ on $\Omega^e$.
This form allows all operator evaluations to be expressed as {\em fast tensor
contractions}, which can be implemented as BLAS3 operations\footnote{For
example, with $\Dh_{il} := \dd{h_l}{r} |^{}_{\xi_i}$,
the first derivative takes the form $u_{r,ijk}=\sum_l \Dh_{il} u_{ljk}$,
which is readily implemented as an $N_p \times N_p$ matrix times
an $N_p \times N_p^2$ matrix, with $N_p=N+1$.}
in only $O(N^4)$ work and $O(N^3)$ memory references \cite{dfm02,sao80}.
This low complexity is in sharp
contrast to the $O(N^6)$ work and storage complexity of the
traditional $p$-type FEM.  Moreover, hexahedral (hex) element function
evaluation is about six times faster per degree-of-freedom (dof) than
tensor-based tetrahedral (tet) operator evaluation \cite{moxey20}.
By diagonalizing one direction at a time, the SEM structure admits
fast block solvers for local Poisson problems in undeformed and (approximately)
in deformed elements, which serve as local smoothers for $p$-multigrid (pMG)
\cite{lottes05}.

$C^0$ continuity implies that the SEM is {\em communication minimal:}
data exchanges have unit-depth stencils, independent of $N$.
Finally, local $i$-$j$-$k$ indexing avoids much of the indirect addressing
associated with fully unstructured approaches, such that high-order SEM
implementations can
realize significantly higher throughput (millions of dofs per second, MDOFS)
than their low-order counterparts \cite{ceed_bp_paper_2020}.

%%% \input tex/figscale_crop

\paragraph{Performance on Aurora and Frontier.} 
%From the logfile timing data, we plot strong-scaling performance in Fig.
%\ref{fig:scale} for a flow through a single $17 \times 17$ rod bundle of a
%fission reactor for $E=4709$K elements of order $N=7$ ($n$=1.6B gridpoints).
%Shown in the top row are measured values of the time-per-step for three
%platforms: OLCF's Frontier, which features AMD MI250X GPUs, each having two MPI
%ranks (one per GCD); ALCF's NVIDIA A100-based Polaris (one rank per A100); and
%ALCF's Aurora, which has Intel PVC GPUs, each running two MPI ranks (one per
%tile).  We plot the performance as a function of $P$, the number of MPI ranks,
%in the upper left, and as a function of $n/P$ on the upper right.  Because it
%factors out problem size, the number of points per rank is somewhat more
%universal than the number of ranks as an independent variable
%\cite{ceed_bp_paper_2020}.  The plots show that Polaris is about $2\times$
%faster than Aurora, per rank and about $1.5 \times$ faster than Frontier.  We
%expect that the Aurora numbers will improve as network issues are sorted out.
%%
%%The center row shows the parallel efficiency. We see that, for this case,
%%
%Inspection of the data reveals that
%Frontier realizes $\approx 80$\% efficiency at $n_{0.8}=n/P=4$M points per
%rank, whereas Polaris has $n_{0.8} = 5$M, and Aurora has $n_{0.8}=7$M.  
%Larger values of $n_{0.8}$ imply that one has to use fewer processors, and thus
%run slower, to maintain 80\% efficiency. (Small $n_{0.8}$ is better.)  In all
%likelihood, Aurora's numbers will improve once this early system is debugged.
%
%
%The last row of Fig. \ref{fig:scale} breaks out the costs of some of the
%leading performance bottlenecks.  On the lower left, we plot the time-per-step
%for the nonlinear advection evaluation, {\tt makef}.  We see that Aurora spends
%roughly twice the amount of time in this kernel than either Frontier or
%Polaris.  This kernel shows perfect linear scaling because it is compute
%intensive and almost devoid of communication.  We speculate that the relatively
%poor performance of Aurora stems from cache effects on the PVC.  Because
%advection is dealiased with the 3/2's rule, the working data set per element is
%$12^3$, rather than $8^3$, which is the size for the majority of the other
%elemental operations.  Experiments in which we reduce the order of dealising
%from 12 to 9 for this case led to a 1.5$\times$ reduction in advection time,
%but this is not as dramatic an improvement as one might expect when cache
%spilling is alleviated.  We note that the majority of the Aurora kernel
%performance is on par with Frontier.

\input tex/tables
\input tex/figs

%\subsubsection{MHD performance study}

%\input tex/mhd_performance



