\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{Advancing Fusion and Fission Energy through Exascale} \rhead{E. Merzari et al.} \renewcommand{%
\headrulewidth}{0.0pt}

\centering {\bf Curriculum Vitae }\\
{\bf PAUL FISCHER}\\
{\bf e-mail: fischerp@illinois.edu, phone: +1(217) 300-2031}\\
{\bf e-mail: fischer@mcs.anl.gov, phone: +1(630) 252-6018}\\
 \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt

Ph.D., 1989, Mechanical Engineering, Massachusetts Institute of Technology \\
M.S., 1982, Mechanical Engineering, Stanford University \\
B.S., 1981, Mechanical Engineering, Cornell University \\
}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt

2014--present, Blue Waters Professor, CS \& MechSE, University of Illinois, Urbana-Champaign \\
2014--present, Senior Scientist (part time), Mathematics and Computer Sci. Div., Argonne Nat. Lab.\\
2008-2014, Senior Scientist, Mathematics and Computer Sci. Div., Argonne Nat. Lab. \\
2009-2014, Professor (part-time), Dept. of Statistics, University of Chicago \\
2003-2008, Adjunct Faculty, Dept. of Mech. Eng., University of Illinois, Chicago \\
1999-2014, Senior Fellow, Computation Institute, University of Chicago \\
1998-2008, Mathematician, Mathematics and Computer Sci. Div., Argonne Nat. Lab. \\
1991-1998, Assistant Professor, Div. of Applied Mathematics, Brown U. \\
1990-1991, Postdoctoral Position in Applied Mathematics, Caltech \\
1986-1989, Research Assistant in Mechanical Eng., M.I.T. \\
1983-1986, Sr. Mechanical Engineer, Digital Equipment Corporation \\
1981-1982, Research Assistant in Mechanical Eng., Stanford U./NASA Ames \\
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item P.~Fischer, S.~Kerkemeier, M.~Min, Y.H. Lan, M.~Phillips, T.~Rathnayake,
      E.~Merzari, A.~Tomboulides, A.~Karakus, N.~Chalmers, and T.~Warburton.
      Nek{RS}, a {GPU}-accelerated spectral element {Navier-Stokes} solver.
      {\em CoRR}, abs/2104.05829, 2021. \\
\item M.O. Deville, P.F. Fischer, and E.H. Mund. High-order methods for incompressible fluid flow.
      Cambridge University Press, Cambridge, 500 p., 2002. \\
\item D.~Giannakis, R.~Rosner, and P.~Fischer.  Linear stability analysis of
      incompressible magnetohydrodynamic flows with a free surface.  {\em J. Fluid
      Mech.}, 636:217--277, 2009. \\
\item D.~Giannakis, P.~Fischer, and R.~Rosner.  A spectral {Galerkin} method for the
      coupled {Orr-Sommerfeld} and induction equations with free-surface
      boundary-conditions.  {\em J. Comput. Phys.}, 228:1188--1233, 2009. \\
\item H.M. Tufo and P.F. Fischer. Terascale spectral element algorithms and implementations. In Proc.
      of the ACM/IEEE SC99 Conf. on High Performance Networking and Computing, Gordon Bell
      Prize. IEEE Computer Soc., CDROM, 1999. 
\end{enumerate}

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt

High-Order Numerical Methods for Partial Differential Equations, Scalable Parallel Algorithms, Iterative Solvers, Parallel Computing, Spectral Element Methods, Computational Fluid Dynamics
}

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
%
 \item With the help of collaborators and support from DOE's programs in
Applied Math Research and the DOE ECP Center for Efficient Exascale
Discretizations (CEED), we have developed advanced high-order algorithms and
deployed these in the scalable open-source Navier-Stokes codes, Nek5000 and
NekRS, which have over 400 users (https://nek5000.mcs.anl.gov). In addition to
providing a scalable high-order accuracy simulation engine, the source
distribution provides researchers with direct access to advanced parallel
algorithms and implementations capable of scaling to millions of processors and
billions of gridpoints. \\
%
\item Deputy Director, CEED.
%
\item Reviewer for J.Comp. Phys., SISC, J. Fluid Mech., J. Sci. Comp., SINUM, Nucl. Eng. Des. \\
%
 \item Gordon Bell Prize for High-Performance Computing, 1999
%
 \item 2021 \& 2022 DOE INCITE Award
%
 \item R\&D 100 Award, 2016
%
 \item University of Chicago Distinguished Performance Award, 2009
%
 \item Fellow of American Association for the Advancement of Science (AAAS), 2012
%
 \item First recipient, Center for Research on Parallel Computation Prize Fellowship, Caltech, 1990
\end{enumerate}

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})}
{\parindent 16pt


 S. Balachandar, (U. Florida), \\
 Natalie Beams, (UTK), \\
 Jed Brown, (UC Boulder), \\
 Veselin Dobrev, (LLNL), \\
 Jack Dongarra  (UTK), \\
 Chistos Frouzakis (ETH Zurich), \\
 Jason Hackl   (U. Florida),  \\
 Yassin Hassan (TAMU),  \\
 Tzanio Kolev (LLNL),  \\
 Elia Merzari (PSU), \\
 Robert Moser (UT Austin), \\
 Murtazo Nazarov (Uppsala), \\
Alexandr Obabko (ANL) \\
 Tamay \"Ozg\"okmen (U. Miami),  \\
Anthony Patera (MIT) \\
Carlos Pantano (USC) \\
Ken Raffenetti (ANL) \\
%Janet Scheel (Occidental), \\
 Philipp Schlatter (KTH), \\
 Andrew Siegel     (ANL), \\
 Mark Shephard     (RPI), \\
 Phillipe Spalart (Boeing), \\
 Michael Sprague (NREL), \\
Ananias Tomboulides (AUT) \\
 Tim Warburton (VT) \\
 }


\end{flushleft}

\end{document}
