\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{Advancing Fusion and Fission Energy through Exascale} \rhead{E. Merzari et al.} \renewcommand{%
%\pagestyle{fancy} \lhead{Harnessing Exascale: First of a Kind High Fidelity Full Core Simulations} \rhead{E. Merzari et al.} \renewcommand{%
%\pagestyle{fancy} \lhead{Large Eddy Simulation of Rod Bundle Cores} \rhead{E. Merzari et al.} \renewcommand{%
\headrulewidth}{0.0pt}

\centering {\bf Curriculum Vitae}\\
{\bf ELIA MERZARI}\\
{\bf e-mail: ebm5351@psu.edu, phone: +18148637469} \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt
   ~\\
   Ph.D., 2008, Tokyo Institute of Technology (Japan), Nuclear Engineering \\
   M.S.,  2005, Politecnico di Milano (Italy), Nuclear Engineering \\
   B.S.,  2003, Politecnico di Milano (Italy), Mechanical/Energy Engineering \\
}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt
  ~\\
  2019--present, Associate Professor, Pennsylvania State University\\
  2014--2019, Principal Nuclear Engineer, Argonne National Laboratory \\
  2010--2014, Nuclear Engineer, Argonne National Laboratory \\
  2009--2010, Post-doctoral Researcher, Argonne National Laboratory\\
  2008--2009, JSPS Fellow,  Tokyo Institute of Technology\\
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item E. Merzari, P. Fischer and W.D. Pointer. Numerical Simulation and Proper
  Orthogonal Decomposition of the flow in a Counter-Flow
  T-junction. \textit{Journal of Fluids Engineering}, {\bf 135}, 091304, 2013.
\item J. Walker, E. Merzari, A. Obabko, P. Fischer and A. Siegel. Accurate Prediction of the Wall Shear Stress in Rod Bundles with the Spectral Element Method at High Reynolds Numbers. \textit{International Journal of Heat and Fluid Flow}, {\bf 50}, 287--299, 2014.
\item E. Merzari, J. G. Smith, A. Tentner, W. D. Pointer, and P. Fischer. Numerical simulation of the flow in wire-wrapped rod-bundles: Effect of wire-pin contact modeling. \textit{Nuclear Engineering and Design}, {\bf 253}, 364--386, 2012.
\item E. Merzari, P. Fischer and  J. Walker. Large-Scale Simulation of Rod Bundles: Coherent Structure Recognition and Stability Analysis. \textit{Proceedings of the ASME-JSME-KSME Joint Fluids Engineering Conference 2015}, Seoul, South Korea, American Society of Mechanical Engineers, 2015.
\item E. Merzari and P. Fischer. Controlling Turbulence in Tight Rod Bundles. \textit{Proceedings of the Fluids Engineering Summer Meeting 2013}, Incline Village, NV, American Society of Mechanical Engineers, 2013.
\end{enumerate}

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt
Computational Fluid Dynamics, Linear Stability Analysis, Proper Orthogonal Decomposition, Flow-Induced Vibrations, Nuclear Reactor Thermal-hydraulics.
}

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Recipient of the 2014 American Nuclear Society (ANS) Landis Young Member Engineering Achievement Award.
\item Recipient of the 2016 George Westinghouse Silver Medal (ASME).
\item Recipient of the 2014 HPC forum HPC Innovation Excellent Award.
\item Past Chair of the Computational Fluids Dynamics Technical Committee of the Fluids Engineering Division of the American Society of Mechanical Engineers (ASME).
\item Vice-Chair of the Thermal-hydraulic division of the American Nuclear Society.
\end{enumerate}

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})}
{\parindent 16pt
~\\
\textbf{E. Baglietto}, MIT, USA;  \textbf{E. Balaras}, G. Washington University, USA;  \textbf{P. Bardet}, G. Washington University, USA;  \textbf{X. Cheng}, KIT, Germany;  \textbf{E. Colombo}, Politecnico di Milano, Italy;  \textbf{B. Ferencz}, Lawrence Livermore National Laboratory, USA;  \textbf{P. Fischer}, Argonne National Laboratory, USA;  \textbf{Y. Gohar}, Argonne National Laboratory, USA;  \textbf{V. Gopala}, NRG, Netherlands;  \textbf{Y. Hassan}, Texas A\&M, USA;  \textbf{F. Inzoli},  Politecnico di Milano, Italy; \textbf{R. Jain}, Argonne National Laboratory, USA;  \textbf{A. Khakim}, \textit{unknown};  \textbf{V. Mahadevan}, Argonne National Laboratory, USA;  \textbf{R. Mereu}, Politecnico di Milano, Italy;  \textbf{H. Ninokata}, Politecnico di Milano, Italy;  \textbf{A. Obabko}, Argonne National Laboratory, USA;  \textbf{W. D. Pointer}, Oak Ridge National Laboratory, USA;  \textbf{F. Roelofs}, NRG, Netherlands;  \textbf{A. Siegel}, Argonne National Laboratory, USA; \textbf{J. G. Smith}, CD-Adapco, USA; \textbf{M. A. Smith}, Argonne National Laboratory, USA;  \textbf{K. Smith}, MIT, USA; \textbf{T. Sofu}, Argonne National Laboratory, USA; \textbf{T. Tautges}, Argonne National Laboratory, USA;  \textbf{S. Tavoularis}, University of Ottawa, Canada;  \textbf{A. Tentner}, Argonne National Laboratory, USA;  \textbf{A. Tomboulides}, Argonne National Laboratory, USA; \textbf{K. Van Tichelen}, SCK, Belgium; \textbf{J. Walker}, University of Wisconsin, USA;  \textbf{K. Walters}, Mississippi State University, USA;  \textbf{P. Ward}, Texas A\&M, USA; \textbf{E. Wolters}, Argonne National Laboratory, USA;  \textbf{Z. Zhong}, Argonne National Laboratory, USA.
}

\end{flushleft}

\end{document}
