
\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{Advancing Fusion and Fission Energy through Exascale} \rhead{E. Merzari et al.} \renewcommand{%
% \pagestyle{fancy} \lhead{Harnessing Exascale: First of a Kind High Fidelity Full Core Simulations} \rhead{E. Merzari et al.} \renewcommand{%
% \pagestyle{fancy} \lhead{Large Eddy Simulation of Rod Bundle Cores} \rhead{E. Merzari et al.} \renewcommand{%
\headrulewidth}{0.0pt}

\centering {\bf Curriculum Vitae }\\
{\bf MISUN MIN}\\
{\bf e-mail: mmin@mcs.anl.gov, phone: +1(630)252-5380} \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt

Ph.D., 2003, Applied Mathematics, Brown University \\
M.S. 1997, Applied Mathematics, Brown University \\
M.S./B.S. 1993/1991, Mathematics, Hanyang University, South Korea \\
}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt

2011--present, Computational Mathematician, Argonne National Laboratory \\
2006--2011, Assistant Computational Scientist, Argonne National Laboratory\\
2003-2006, Postdoctoral Researcher, Argonne National Laboratory\\
%2003, Research Associate, Applied Mathematics, Brown University \\
%1998-2002, Research Assistant, Applied Mathematics, Brown University \\
%1997, Teaching Assistant, Applied Mathematics, Brown University\\
1994-1996, Mobile Communication System Researcher, Hyundai Electronics, South Korea\\
%1991-1993, Teaching Assistant, Mathematics, Hanyang University, South Korea \\
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt

 \item
  Fischer P, Kerkemeier S, Min M, Lan Y, Phillips M, Rathnayake T, Merzari E, Tomboulides A, Karakus A, Chalmers N, Warburton T. https://arxiv.org/abs/2210.00904. Parallel Computing. 2022 December; 114:102982. Available from: https://doi.org/10.1016/j.parco.2022.102982
   
 \item
  Fischer P, Min M, Rathnayake T, Dutta S, Lolev T, Dobrev V, Camier J, Kronbichler M, Warburton T, Swirydowicz K, Brown J. Scalability of high-performance PDE solvers. The International Journal of High Performance Computing Applications. 2020 June 15; 34(5):562- 586. Available from: https://doi.org/10.1177/109434202091576

 \item
  Kolev T, Fischer P, Min M, Dongarra J, Brown J, Dobrev V, Warburton T, Tomov S, Shephard M, Abdelfattah A. Efficient exascale discretizations: High-order finite element methods. International Journal of High Performance Computing Applications. 2021 November 01; 35(6):527-552. Available from: https://doi.org/10.1177/109434202110208

 \item
  Min M, Lan Y, Fischer P, Merzari E, Kerkemeier S, Phillips M, Rathnayake T, Novak A, Gaston D, Chalmers N, Warburton T. Optimization of full-core reactor simulations on summit. 2022 SC22: International Conference for High Performance Computing, Networking, Storage and Analysis (SC). 2022 November 03; :1067-1077. Available from: 10.1109/SC41404.2022.00079
 
 \item
  Merzari E, Fischer P, Min M, Kerkemeier S, Obabko A, Shaver D, Yuan H, Yu Y, Martinez J, Brockmeyer L, Fick L, Busco G, Yildiz A, Hassan Y. Toward exascale: overview of large eddy simulations and direct numerical simulations of nuclear reactor flows with the spectral element method in Nek5000. Nuclear Technology. 2020 June 25; 206(9):1308-1324. Available from: https://doi.org/10.1080/00295450.2020.1748557

%\item
%  Paul Fischer, Elia Merzari, Misun Min, Stefan Kerkemeier, Yu-Hsiang Lan, Malachi Phillips, Thilina Rathnayake, April Novak, Derek Gaston, Noel Chalmers, Tim Warburton,
%  Highly Optimized Full-Core Reactor Simulations on Summit,
%  accepted to \textit{Supercomputing 2022}.\\ 
%\item
%  Paul Fischer, Stefan Kerkemeier, Misun Min, Yu-Hsiang Lan, Malachi Phillips, Thilina Rathnayake, Elia Merzari, 
%  Ananias Tomboulides, Ali Karakus, Noel Chalmers, Tim Warburton,
%  NekRS, a GPU-Accelerated Spectral Element Navier-Stokes Solver,
%  revision, \textit{Parallel Computing}, 2022. (arXiv:2104.05829)\\
%\item Paul Fischer, Misun Min, Thilina Rathnayake, Som Dutta, Tzanio Kolev, Veselin
%  Dobrev, Jean-Sylvain Camier, Martin Kronbichler, Tim Warburton, Kasia
%  Swirydowicz, and Jed Brown, Scalability of high-performance PDE solvers,
%  \textit{Int. J. High Perf. Comput. Appl.}, vol. 34, 5. pp. 562--586, 2020. \\
%% \item Martinez Rubio, Javier, Yu-Hsiang Lan, Elia Merzari and Misun Min,
%% On the use of LES-based turbulent thermal-stress models for rod bundle simulations,
%% \textit{International Journal of Heat and Mass Transfer}, 142, 118399, 2019. \\
%\item Matthew Otten, Jing Gong, Azamat Mametjanov, Aaron Vose, Paul Fischer, and Misun Min,
%Hybrid MPI/OpenACC implementation for a high order electromagnetic solver on GPUDirect communication,
%\textit{International Journal of High Performance Computing Applications}, Vol. 30, No.3, pp.320--334, 2016.\\
%\item Paul Fischer, Katherine Heisey, and Misun Min, Scaling limits for PDE-based simulation (Invited),
%\textit{22nd AIAA Computational Fluid Dynamics Conference, AIAA Aviation} (2015-3049), 2015.
\end{enumerate}

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt
Numerical PDEs, High-Order Methods, 
%High-Performance Computing, 
Scalable Algorithms,
Large-Scale Simulations, Performance Analysis, 
%Exascale Applications, %Large-Scale Simulations, High-Performance Computing,
Multiphysics Applications,
%High-Order Spectral Element/Discontinuous Galerkin Methods,
%Jacobian-Free Newton Krylov Methods,
Computational Electromagnetics, Computational Fluid Dynamics
}

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
 \item 2021 \& 2022 DOE INCITE Award
 \item Recipient of 2016 R\&D 100 on "NekCEM/Nek5000: Scalable High-Order Simulation Codes"
 \item Keynote Lecturer at NahomCon 2017, ICOSAHOM 2023, ParCFD2023.
 \item Reviewer for DOE-ASCR, DOE-SBIR, NSF-CFD, NSF-Numerical PDEs.
 \item Reviewer for SC 16/18/21 and ATPESC 2020/2021/2022/2023.
 \item Mentored 24 summer interns at Argonne National Laboratory.
 \item Open-source contributions and large-scale performance: NekCEM, NekLBM, Nek5000, NekRS
%
%\item 2021 \& 2022 DOE INCITE Award
%\item Recipient of 2016 R\&D 100 on "NekCEM/Nek5000: Scalable High-Order Simulation Codes"
%\item Argonne PI of ECP Co-Design Center for Efficient Exascale Discretizations (CEED)
%\item NSF CFD Review Panel (2019), NSF Numerical PDEs Review Panel (2012) 
%\item SC21 Workshop Program Committee; SC18 \& SC16 Technical Paper Review Committee  
%\item ATPESC 2022/2021/2020 Review Committee
%\item Argonne LCRC Allocation Committee
%\item Reviewer for Int. J. High Perf. Comp. App.,
%J. Optics, J. Comp. Phys.,
%J. Sci. Comp., J. Comp. App. Math., App. Numer. Math., SIAM J. Sci. Comp.
\end{enumerate}

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})}
{\parindent 16pt

Paul Fischer (UIUC/ANL),\\
Tzanio Kolev (LLNL), \\
Ananias Tomboulides (AUTH/ANL),\\
Stefan Kerkemeier (K2/ANL),\\
Oriol Lehmkuhl (BSC),\\
Haomin Yuan (ANL),\\
Stephen Gray (ANL),\\
Kris Rowe (ANL),\\
Tim Warburton (VT), \\
Tzanio Kolev (LLNL), \\
Vishal Kumar (ANL),\\
Kotamarthi Rao (ANL), \\
Dahai Guo (Intel), \\
Miwako Tsuji (RIKEN), \\ 
Mitsuhisa Sato (RIKEN),\\
Martin Kronbichler (TUM, Germany), \\
Veselin Dobrev (LLNL), \\
Jed Brown (UC Boulder), \\
%Fadil Santosa (U Minnesota), \\
%Josh Wilson (U Minnesota), \\
%Tony Low (U Minnesota), \\
Michael Sprague (NREL),\\
Michael Brazell (NREL), \\
Matthew Churchfield (NREL), \\
Jun Fang (ANL),\\
%Javier Rubio (Scuderia Toro Rosso),\\
Som Dutta (Utah State),  \\
Jing Gong (KTH/Sweden), \\
%Yongjoon Hong (SDSU), \\
%YuHsiang Lan (ANL), \\
Saumil Patel (ANL), \\
Taehun Lee (CUNY), \\
%Tai-Chia Lin  (NTU/Taiwan), \\
Elia Merzari (PSU/ANL), \\
David Nicholls (UIC) \\
Aleksandr Obabko (ANL)}   
%Evelyn Otero (KTH/Sweden), \\
%Matthew Otten (ANL). }


\end{flushleft}

\end{document}
